RFMO Initial Analysis

### 2019-09-10 RFMO Analysis.Rmd
Created an extra file for RFMO and worked some plots

---
title: "Initial Analysis"
author: "Juliano Palacios-Abrantes"
date: '2019-02-04'
output: html_document
editor_options: 
  chunk_output_type: console
---

>>>>

---
title: "RFMO Initial Analysis"
author: "Juliano Palacios-Abrantes"
date: '2019-02-04'
output: html_document
editor_options: 
  chunk_output_type: console
---
